Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-13 prop_iop.tex
prop_iop.tex \section{Quantum and Classical Interval-valued Probability Measures} Updating...

In this section, we are going to discuss the relation between quantum
and classical. We first prove that any quantum phenomenon would not
be observed if we could only access commuting projectors since we
can pick a common basis to measure mutually commuting observables
simultaneously~\cite{Mermin_1993}. Based on this fact, we show a
quantum IVPM~$\bar{\mu}$ is convex if its restriction on any orthonormal
basis~$\Omega$, $\bar{\mu}^{\Omega}$ is a convex classical IVPM.
Together with the fact that every classical IVPM~$\bar{\mu}^{\Omega}:2^{\Omega}\rightarrow\mathscr{I}$
is convex when the number of elements in $\Omega$ is less than or
equal to 3, every quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
must be convex on a three-dimensional Hilbert space.

Before we dive into the lemmas and proofs, we start from two definitions.

@@

\begin{proof}When $\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$,
$\bar{\mu}$ and $\bar{\mu}^{\Omega}$ are essentially quantum and
classical real-valued probability measures, respectively. Hence, it
is sufficient to prove the interval-valued case.
\begin{itemize}
\item $\bar{\mu}^{\Omega}(\emptyset)=\bar{\mu}\left(\sum_{\ket{j}\in\emptyset}\proj{j}\right)=\bar{\mu}\left(\mathbb{0}\right)=[0,0]$. 
\item $\bar{\mu}^{\Omega}(\Omega)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)=[1,1]$. 
\item For any event $E$,
\begin{equation}\eqalign{ 
\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)&=\bar{\mu}\left(\sum_{\ket{j}\in\Omega\backslash E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)\\
&=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .} 
}\end{equation}commuting
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, we have
\begin{equation}\eqalign{ 
\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)&=\bar{\mu}\left(\sum_{\ket{j}\in\bigcup_{i=1}^{N}E_{i}}\proj{j}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\\
&\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)\textrm{ .} 
}\end{equation}
\end{itemize}
\end{proof}

The previous lemma suggests that given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
if we only consider the events generated by $\Omega$, $\events^{\Omega}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
then any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
behaves classically when restricting the domain on $\events^{\Omega}$,
i.e., consider $\bar{\mu}|_{\events^{\Omega}}$. In particular, if
$\bar{\mu}$ is convex, each $\bar{\mu}|_{\events^{\Omega}}$ has
a non-empty core. However, the core elements of each $\bar{\mu}|_{\events^{\Omega}}$
may not be glued together, and gives a core element of $\bar{\mu}$.
The inability of gluing core elements among commuting $\events^{\Omega}$
to non-commuting $\events$ is consistent with the idea of the Kochen-Specker
theorem, that each triple of commuting observables could be colored
well, but we cannot color all observables which are not all commuting.
This is also consistent with the assertion that mutually commuting
observables could be measured simultaneously~\cite{Mermin_1993}.
In another word, if Alice and Bob in Bell's theorem can only pick
from a set of mutually commuting observables, they could never observe
any ``quantum,`` and we cannot eliminate the local hidden variable
theory in this setting.

>>>>

This section discusses the relation between quantum and classical.
We first prove that any quantum phenomenon would not be observed if
we could only access commuting projectors since we can pick a common
basis to measure mutually commuting observables simultaneously~\cite{Mermin_1993}.
Based on this fact, we show a quantum IVPM~$\bar{\mu}$ is convex
if its restriction on any orthonormal basis~$\Omega$, $\bar{\mu}^{\Omega}$,
is a convex classical IVPM. Together with the fact that every classical
IVPM~$\bar{\mu}^{\Omega}$ is convex when the number of elements
in $\Omega\le3$, every quantum IVPM must be convex on a three-dimensional
Hilbert space.

Before diving into the lemmas and proofs, we start from two definitions.

@@

\begin{proof}When $\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$,
$\bar{\mu}$ and $\bar{\mu}^{\Omega}$ are essentially quantum and
classical real-valued probability measures, respectively. Hence, it
is sufficient to prove the interval-valued case.
\begin{itemize}
\item $\bar{\mu}^{\Omega}(\emptyset)=\bar{\mu}\left(\sum_{\ket{j}\in\emptyset}\proj{j}\right)=\bar{\mu}\left(\mathbb{0}\right)=[0,0]$. 
\item $\bar{\mu}^{\Omega}(\Omega)=\bar{\mu}\left(\sum_{\ket{j}\in\Omega}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}\right)=[1,1]$. 
\item For any event $E\in2^{\Omega}$,
\begin{equation}\eqalign{ 
\bar{\mu}^{\Omega}\left(\Omega\backslash E\right)&=\bar{\mu}\left(\sum_{\ket{j}\in\Omega\backslash E}\proj{j}\right)=\bar{\mu}\left(\mathbb{1}-\sum_{\ket{j}\in E}\proj{j}\right)\\
&=\bar{\mu}\left(\mathbb{1}\right)-\bar{\mu}\left(\sum_{\ket{j}\in E}\proj{j}\right)=\left[1,1\right]-\bar{\mu}^{\Omega}\left(E\right)\textrm{ .} 
}\end{equation}
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}\subseteq2^{\Omega}$
of pairwise disjoint events, we have
\begin{equation}\eqalign{ 
\bar{\mu}^{\Omega}\left(\bigcup_{i=1}^{N}E_{i}\right)&=\bar{\mu}\left(\sum_{\ket{j}\in\bigcup_{i=1}^{N}E_{i}}\proj{j}\right)=\bar{\mu}\left(\sum_{i=1}^{N}\sum_{\ket{j}\in E_{i}}\proj{j}\right)\\
&\subseteq\sum_{i=1}^{N}\bar{\mu}\left(\sum_{\ket{j}\in E_{i}}\proj{j}\right)=\sum_{i=1}^{N}\bar{\mu}\left(E_{i}\right)\textrm{ .} 
}\end{equation}
\end{itemize}
\end{proof}

By the previous lemma, given an orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$,
if we only consider the events generated by $\Omega$, $\events^{\Omega}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
then any quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
behaves classically when restricting the domain on $\events^{\Omega}$,
i.e., consider $\bar{\mu}|_{\events^{\Omega}}$. In particular, if
$\bar{\mu}$ is convex, each $\bar{\mu}|_{\events^{\Omega}}$ is convex
and has a non-empty core. However, the core elements of each $\bar{\mu}|_{\events^{\Omega}}$
may not be glued together, and gives a core element of $\bar{\mu}$.
The inability of gluing core elements among commuting $\events^{\Omega}$
to non-commuting $\events$ is consistent with the idea of the Kochen-Specker
theorem, that each triple of commuting observables could be colored
well, but we cannot color all observables which are not all commuting.
This is also consistent with the assertion that mutually commuting
observables could be measured simultaneously~\cite{Mermin_1993}.
In another word, if Alice and Bob in Bell's theorem can only pick
from a set of mutually commuting observables, they could never observe
any ``quantum,`` and we cannot eliminate the local hidden variable
theory in this setting.
